---
title: "bpmn - BPMN diagrams in R"
output: 
  html_document: 
    keep_md: yes
    self_contained: no
    theme: spacelab
---

```{r results="asis", echo=FALSE}
cat("
<style>
  .djs-overlay {
    color: red; 
    opacity: 0.8;
    pointer-events: none; 
  }
</style>
")
```


```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, fig.width = 9, fig.height = 2.5)
```

## Overview
bpmn is an R interface to the [bpmn-js](https://github.com/bpmn-io/bpmn-js) library (a BPMN 2.0 rendering toolkit and web modeler) from [bpmn.io](https://bpmn.io/). Using JavaScript in R is handled by [htmlwidgets](http://www.htmlwidgets.org/) framework. 

## Installation 
Install from GitHub:

```{r, eval=FALSE}
devtools::install_github("bergant/bpmn")
```


## Display a BPMN diagram

```{r}
library(bpmn)
```


Use `bpmn` widget with a BPMN file:

```{r}
bpmn_file <- system.file("examples/qr-code.bpmn", package = "bpmn")
bpmn(bpmn_file)
```

## Elements in the diagram

With `bpmn_get_elements` function it is possible to get BPMN elements
with names and I:

```{r}

library(xml2)
elements <- bpmn_get_elements(read_xml(bpmn_file))

library(htmlTable)
htmlTable(elements, align = "lll", rnames = FALSE, css.class = "table")

```


## Overlays

We can add additional notes aside any element of the 
diagram.

```{r }
overlays <- list(
  
  overlay(
    element = "SCAN_OK", 
    html = "Mixed up the labels?"
  ),
  overlay(
    element = "sid-52EB1772-F36E-433E-8F5B-D5DFD26E6F26", 
    html = "Manually?",
    top = -40,
    left = -40
  )
)

bpmn(bpmn_file, overlays = overlays)
```

## More

There are a lot of bpmn-js features (e.g. designing a new diagram) which are not 
(yet) supported by this widget. Explore these on [bpmn.io demo site](http://demo.bpmn.io/).


## Project

GitHub: https://github.com/bergant/bpmn

Issues: https://github.com/bergant/bpmn/issues


## Licenses

bpmn package: MIT License

See [license file](https://github.com/bergant/bpmn/blob/master/inst/htmlwidgets/lib/bpmn-js/LICENSE) for the included **bpmn-js** library
